Paper on the carbonate chemistry at Ny-Ålesund

### 2020-12-28 paper.Rmd
clean up and chnaged variable names

```{r read and clean data, echo=FALSE, warning=FALSE, message=FALSE}
  # d_all <- readRDS(file = paste0(path_data, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour_copy.rds"))
# d <- d_all %>% 
#   as_tsibble(index = datetime) %>% 
#   dplyr::rename(depth = pressure_insitu_ctd) %>% 
#   dplyr::mutate(year_month = format(datetime, '%Y-%m'))
# count_gaps(d, .full = TRUE)

d_all <- readRDS(file = paste0(path_data, "fb_data/d_all.rds"))
d <- d_all %>% 
  as_tsibble(index = datetime) %>% 
  dplyr::arrange(datetime) %>%
  fill_gaps() %>%
  dplyr::mutate(year_month = format(datetime, '%Y-%m'),
                quarter = quarter(datetime)) %>%
  replace(., is.na(.), NA) # replace NaN by NA everywhere
```

@@

d_ts <- d %>%
  #dplyr::mutate(pHint_tot_sf = ifelse(depth >= 8, pHint_tot_sf, NA)) %>% # keep only seafet data below 8 m depth
  dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air, pco2_corr,
                pHint_tot_sf_9m, ph_s_sf_temp_insi, at_calc, at) #%>%
  #tidyr::pivot_longer(-datetime, values_to = "value")

@@

# PCO2 
ts_pCO2 <- d_all %>%
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pco2_corr), 
             colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  geom_point(aes(x = datetime, y = pco2_calc_fb), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="Mesured (blue) and calculated (CT+AT; red) pCO2",x="", y="pCO2 (uatm)") +
  Mytheme(size_labs = 8)

@@

ts_pCO2_bp <- d_all %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pco2_contros)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm=TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", 
               outlier.size = 0.3, na.rm=TRUE) +
  labs(y = expression(paste(pCO[2])), x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank())

@@

Salinity <- qq(d_all$sal_fb, digits=1)
Temperature <- qq(d_all$temp_fb, digits=1)
pCO2 <- qq(d_all$pco2_contros, digits=1)
pH <- qq(d_all$pHint_tot_sf, digits=3)
AT <- qq(d_all$at_calc, digits=1)
tab_quartiles <- as_tibble(rbind(Salinity, Temperature, pCO2, pH, AT)) %>%
  rename("2.5%"=V1, "50%"=V2, "97.5%"=V3) %>%
  mutate(Variable=c("Salinity", "Temperature", "pCO2", "pH", "AT")) %>%
  dplyr::select(Variable, everything())
kable(tab_quartiles, caption = "Key quantiles") %>%
  kable_styling(full_width=FALSE, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

>>>>

```{r read and clean data, echo=FALSE, warning=FALSE, message=FALSE}
d_all <- readRDS(file = paste0(path_data, "fb_data/d_all.rds"))
d <- d_all %>% 
  as_tsibble(index = datetime) %>% 
  dplyr::arrange(datetime) %>%
  fill_gaps() %>%
  dplyr::mutate(year_month = format(datetime, '%Y-%m'),
                quarter = quarter(datetime)) %>%
  dplyr::rename(pco2_contros = pco2_corr) %>% 
  replace(., is.na(.), NA) # replace NaN by NA everywhere
```

@@

d_ts <- d %>%
  dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air, pco2_contros,
                pHint_tot_sf_9m, ph_s_sf_temp_insi, at_calc, at) #%>%
  #tidyr::pivot_longer(-datetime, values_to = "value")

@@

# PCO2 
ts_pCO2 <- d_all %>%
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pco2_contros), 
             colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  geom_point(aes(x = datetime, y = pco2_calc_fb), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="Mesured (blue) and calculated (CT+AT; red) pCO2",x="", y="pCO2 (uatm)") +
  Mytheme(size_labs = 8)

@@

ts_pCO2_bp <- d_all %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pCO2_contros)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm=TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", 
               outlier.size = 0.3, na.rm=TRUE) +
  labs(y = expression(paste(pCO[2])), x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank())

@@

Salinity <- qq(d_all$sal_fb, digits=1)
Temperature <- qq(d_all$temp_fb, digits=1)
pCO2 <- qq(d_all$pCO2_contros, digits=1)
pH <- qq(d_all$pHint_tot_sf, digits=3)
AT <- qq(d_all$at_calc, digits=1)
tab_quartiles <- as_tibble(rbind(Salinity, Temperature, pCO2, pH, AT)) %>%
  rename("2.5%"=V1, "50%"=V2, "97.5%"=V3) %>%
  mutate(Variable=c("Salinity", "Temperature", "pCO2", "pH", "AT")) %>%
  dplyr::select(Variable, everything())
kable(tab_quartiles, caption = "Key quantiles") %>%
  kable_styling(full_width=FALSE, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```
